mixModelE1data

### 2018-02-27 E1/mixModelE1data.Rmd
mix model initial pilot

Fit mixture model with R (if fitting not previously done and cached). 
```{r, echo=FALSE, message=FALSE, cache=TRUE}
#Setting cache = TRUE in hopes won't have to recalculate estimates "if cached results exist and this code chunk has not been changed since last run" 
library(mixRSVP)

@@

condtnVariableNames <- c("subject","stream", "orientation") #

if (calculate) {
  estimates<- df %>%   filter(subject=="AA") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneCondition(.,numItemsInStream,parameterBounds(),nReplicates=5) )
  estimates<- estimates %>% rename(efficacy = p1, latency = p2, precision = p3)

}
#head(estimates)
```

Unfortunately the differences between MATLAB and R are not trivial. Not substantial either! but we'd prefer trivial.

```{r, echo=FALSE, message=FALSE}
#Compare MATLAB parameter estimates to R
estimates_MATLAB<- estimates_MATLAB %>% rename(efficacy_M = efficacy, latency_M = latency, precision_M = precision, val_M = val)
merged<- merge(estimates,estimates_MATLAB)  
merged<- merged %>% mutate( effDiff = efficacy-efficacy_M, latDiff= latency_M-latency, preDiff= precision_M-precision, negLogL_Diff = val - val_M )

#show differences columns only
diffs<- select(merged, ends_with("Diff"))
```

The mean discrepancy (mean of the absolute value of the difference of the parameter estimates) for
efficacy (effDiff), latency (latDiff), and precision (preDiff) is
```{r, echo=FALSE, message=FALSE}
#calc discrepancies
#Don't include negLogL because absolute value not interpretable
meanDiscrepancy<- diffs %>% select(-negLogL_Diff) 
meanDiscrepancy<- summarise_all(abs(meanDiscrepancy),mean)
round(meanDiscrepancy,3)
```

Now we report the bias difference:  the mean difference without taking the absolute value. Note that the negLogLikelihood for the MATLAB estimates is calculated by R, because Pat's code doesn't save the negative log likelihoods. Also in R we now use integration of the whole area under the bin, whereas Pat used the height of the density function in the center of the bin.
```{r, echo=FALSE, message=FALSE}
biasDiff<- summarise_all(diffs,mean)
round(biasDiff,3)
```
Negative numbers above mean that MATLAB gives slightly higher efficacy and trivially higher precision.
For likelihood, lower neg log likelihood is better, so the negative number means R did better.

>>>>

Fit mixture model with R (if fitting not previously done and cached). 
```{r, echo=FALSE, cache=TRUE}
#Setting cache = TRUE in hopes won't have to recalculate estimates "if cached results exist and this code chunk has not been changed since last run" 
library(mixRSVP)

@@

condtnVariableNames <- c("subject","stream", "orientation")

if (calculate) {
  estimates<- df %>%   filter(subject=="AA") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )
  estimates<- estimates %>% rename(efficacy = p1, latency = p2, precision = p3)

}
head(estimates)
```

Save the param estimates to a file
```{Save param estimates, echo=FALSE}

write.csv(estimates, file = "Data/backwards2E1_paramEstimates")
